\documentclass{article}

\usepackage{fullpage}
\usepackage[parfill]{parskip}
\usepackage{hyperref}

\title{Final Project Proposal}
\author{ASEN 5264}

\begin{document}
    \maketitle

Write a short (less than 1 page, outline is ok) proposal for the Final Project.

Working in a group of up to 3 is highly encouraged! You will submit a single proposal for the entire group.

The proposal should contain the following:
\begin{enumerate}
    \item Problem Statement (e.g. rough formulation as MDP, POMDP, optimization problem, or game)
    \item Description of three methods and corresponding levels of success for solving the problem:
        \begin{enumerate}
            \item A description of a \textbf{minimum working example} that will be the first thing you try. This might be a baseline to compare other approaches against. If you are not able to get this working, you will receive a significant grade penalty.
            \item A description of the \textbf{main approach}. This is an approach that you are confident that you can implement and think will solve the problem well. I will expect to see this implemented successfully in your final report.
            \item A description of a \textbf{stretch goal}. If you have enough time, this is the amazing innovative new solution you will explore.
        \end{enumerate}
\end{enumerate}

Some ideas for final projects can be found here and in the links within: \url{https://github.com/zsunberg/CU-DMU-Materials/blob/master/project/project_ideas.md}.
\end{document}
