\documentclass{article}

\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}
\section*{ASEN 5264 Final Project Report Assignment}

The final assignment for the class is report on your final project. The goal is to produce a paper that is similar to a conference paper (but probably with narrower scope and less novelty).

\subsection*{Formatting}

The length must be between 4 and 8 pages \emph{not including references}. You may include appendices with additional details, but I may not have time to read them. I recommend using the IEEE format - templates can be found here: \url{https://www.ieee.org/conferences/publishing/templates.html}. You may use other formats, but they should be single spaced and have margins similar to the IEEE format (i.e. versions suitable for final submission to a conference rather than drafts).

\subsection*{Target Audience}

The target audience that you should write to is a peer in this class. You can assume the reader will be familiar with the basic concepts introduced in the class, but you should describe the details of the work you did.

\subsection*{Outline}

I recommend using the following outline (you don't have to use this exactly, but all of the info should be included):

\begin{enumerate}[nosep]
    \item Introduction
    \item Background and Related Work
    \item Problem Formulation (make sure to clearly define S, A, T, and R if you are using an MDP example)
    \item Solution Approach
    \item Results (plots and tables - quantify the uncertainty if possible)
    \item Conclusion (and possible Future Work if you want to describe potential extensions)
    \item Contributions and Release (see below)
\end{enumerate}

\section*{Additional Required Items}

\begin{itemize}[nosep]
    \item You must conduct a basic familiarization of literature related to your project. Your report should contain at least 5 citations of related published work and a brief description of how these relate to your project.
    \item At the end of the report include a few sentences about the contributions of each team member (e.g. "Bob collected and cleaned the data, Alice implemented the algorithm", etc.)
    \item At the end of the report, indicate whether you are willing to share the report publicly for other students to benefit from. I highly recommend choosing to share since future students may be able to build off of or be inspired by your work. Please include one of the following release sentences: "The authors grant permission for this report to be posted publicly." or "The authors do NOT grant permission for this report to be posted publicly."
    \item Clearly indicate which algorithms you implemented from scratch vs used off-the-shelf implementations.
\end{itemize}


\end{document}
