\documentclass{article}
\usepackage{fullpage,amsmath,amsthm,graphicx,enumitem,amssymb,booktabs}
\usepackage[hidelinks]{hyperref}
\theoremstyle{definition}
\newtheorem{thm}{Theorem}
\newtheorem{question}[thm]{Question}
\newenvironment{solution}{\noindent\textit{Solution:}}{}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\ttt}[1]{\texttt{#1}}

\title{ASEN/CSCI 5264 Decision Making under Uncertainty\\
       Homework 5: Introduction to POMDPs and Advanced RL}

\begin{document}

\maketitle

\section{Exercises}

\begin{question}(25 points)
    Jill is an entrepreneur of a small business trying to decide whether to commit to sourcing inputs for her business from a domestic supplier or an international supplier. Due to political and legal factors, there is considerable uncertainty about the future of her country's trade policy. This results in a POMDP for Jill. The state space is $S = \{T, F\}$, where $T$ indicates that tariffs will be in effect and $F$ indicates a free trade policy will prevail. The action space is $A = \{D, I\}$, where $D$ indicates that Jill commits to a domestic supplier and $I$ indicates that she commits to an international supplier.
    The reward function is given in the table below:
    \begin{center}
        \begin{tabular}{cc|c}
            \toprule
            $s$ & $a$ & $R(s, a)$ \\
            \midrule
            $T$ & $D$ & 5 \\
            $T$ & $I$ & 2 \\
            $F$ & $D$ & 6 \\
            $F$ & $I$ & 9 \\
            \bottomrule
        \end{tabular}
    \end{center}
\end{question}

\begin{enumerate}[label=\alph*),noitemsep]
    \item Draw or plot the one-step alpha vectors for the one-step plans corresponding to the two actions in the manner done in class. Label each alpha vector with its corresponding action and indicate the rewards for each state.
    \item If Jill believes that tariffs will be found legal with 60\% likelihood, what is the optimal action if the problem only has one step? Justify your answer numerically.
    \item What is the expected reward taking the optimal action given her belief?
\end{enumerate}

Now assume that there is a third action $W$, which corresponds to waiting to see whether tariff or free trade policy will prevail. The wait action has an immediate reward of -1 for any state. After a wait action is taken, a perfectly accurate observation from $O = \{T, F\}$, which reveals the true state, is received.

\begin{enumerate}[label=\alph*),resume,noitemsep]
    \item Draw a diagram depicting a two-step conditional plan where the initial action is $W$ and the subsequent action is $D$ if the observation is $T$ and $I$ if the observation is $F$.
    \item Draw and plot the $\alpha$-vector for this plan on the same axes as the one-step alpha vectors from part (a). \footnote{Drawing the one-step and two step alpha vectors on the same axes is equivalent to saying that problem is infinite-horizon, but terminates after Jill takes a $T$ or $D$ commitment action.} Assume a discount factor of 1.
    \item If Jill's belief is uniform over the two states, indicate which $\alpha$-vector corresponds to the optimal plan and calculate the expected cumulative reward for that plan.
    \item This problem formulation is based on the premise (held by most economists) that tariffs increase costs for businesses that use imported goods directly or in their supply chain, and that Jill cares only about these costs. Suppose that Jill has other concerns, such as a desire to support domestic suppliers. How might this change the problem formulation?
\end{enumerate}

\begin{question}
    (25 pts) Consider the following POMDP that represents cancer monitoring and treatment plan\footnote{Note that the probabilities are not meant to be realistic. See \url{https://pubsonline.informs.org/doi/10.1287/opre.1110.1019} for an actual publication on this topic}:
\begin{eqnarray*}
    \mathcal{S} &=& \left\{\texttt{healthy}, \texttt{in-situ-cancer}, \texttt{invasive-cancer}, \texttt{death}\right\}\\
    \mathcal{A} &=& \left\{\texttt{wait}, \texttt{test}, \texttt{treat}\right\} \quad \mathcal{O} = \left\{\texttt{positive}, \texttt{negative}\right\}\\
    \gamma &=& 0.99 \quad
    s_0 = \texttt{healthy}
\end{eqnarray*}

The \textbf{transition dynamics} are designated with the following table. The state stays the same except with the probabilities encoded in the table.
\begin{center}
\begin{tabular}{ccc}
    \toprule
    $s$ & $a$ & $s'$: $\mathcal{T}(s' \mid s, a)$ \\
    \midrule
    \ttt{healthy} & all & \ttt{in-situ-cancer}: 2\% \\
    \ttt{in-situ-cancer} & \ttt{treat} & \ttt{healthy}: 60\% \\
    \ttt{in-situ-cancer} & $\neq\ttt{treat}$ & \ttt{invasive-cancer}: 10\% \\
    \ttt{invasive-cancer} & \ttt{treat} & \ttt{healthy}: 20\%; \ttt{death}: 20\% \\
    \ttt{invasive-cancer} & $\neq\ttt{treat}$ & \ttt{death}: 60\% \\
    \bottomrule
\end{tabular}
\end{center}

The \textbf{observation} is generated according to the following table. The observation is \ttt{negative} except with the probabilities encoded in the table.
\begin{center}
    \begin{tabular}{ccc}
    \toprule
    $a$ & $s'$ & $o$: $\mathcal{Z}(o \mid a, s')$ \\
    \midrule
    \texttt{test} & \texttt{healthy} & \texttt{positive}: 5\% \\
    \texttt{test} & \texttt{in-situ-cancer} & \texttt{positive}: 80\% \\
    \texttt{test} & \texttt{invasive-cancer} & \texttt{positive}: 100\% \\
    \texttt{treat} & \ttt{in-situ-cancer} or \texttt{invasive-cancer} & \texttt{positive}: 100\% \\
    \bottomrule
    \end{tabular}
\end{center}

The \textbf{rewards} are defined as follows (one could interpret the reward as roughly quality years of life):
\begin{itemize}[noitemsep]
    \item $R(\texttt{death}, \text{any action}) = 0.0$ (i.e. \texttt{death} is a terminal state)
    \item $R(\text{any living state}, \texttt{wait}) = 1.0$
    \item $R(\text{any living state}, \texttt{test}) = 0.8$ (because of costs and anxiety about a positive result)
    \item $R(\text{any living state}, \texttt{treat}) = 0.1$
\end{itemize}

Create a model of this problem using \texttt{QuickPOMDPs} and use Monte Carlo simulations to evaluate a policy that always \textbf{wait}s (we will solve this problem in the next homework).

\end{question}

% \begin{question}
% (25 pts) Using the deep learning library of your choice (e.g. Flux.jl, Knet.jl, Tensorflow, PyTorch), fit a neural network to approximate the function $f(x) = (1-x) \sin(20 \log(x+0.2))$ for the range $x \in [0,1]$. Plot a set of 100 data points fed through the trained model and plot the learning curve (loss vs number of training epochs).
% \end{question}

\clearpage

\section{Challenge Problem}

\begin{question}
    (50 pts) In this exercise, you will learn a policy for the special mountain car environment, \texttt{DMUStudent.HW5.mc}. This environment is a standard mountain car with $\mathcal{A}=[-1, 1]$, except that the observation is a 100x100 matrix. The first two entries in the matrix contain the car's position and velocity. The rest of the matrix may contain useful information to receive additional rewards, but it is not needed to achieve full credit.
    \begin{enumerate}[label=\alph*)]
        \item Implement a reinforcement learning algorithm to learn a policy for the environment that achieves an expected return of at least 40 with discount $\gamma=0.99$, and plot a learning curve. For this part, you must implement the algorithm from scratch and cannot use reinforcement learning packages such as RLLib or OpenAI Baselines, however you can use libraries for components such as neural networks. Write a paragraph describing the algorithm you implemented.\footnote{I recommend discretizing the action space and implementing the DQN algorithm with only the position and velocity - see the starter code for instructions on how to create an environment wrapper to do this; this is the only algorithm that I can provide full debugging support for. DQN should be able to learn a suitable policy in less than 10 minutes of training time on a typical laptop.}\label{q:impl}
        \item Evaluate a policy with \texttt{DMUStudent.HW5.evaluate}, and submit the resulting json file. You may use your code from part (\ref{q:impl} or \emph{any} other libraries for this part. A discount factor of $\gamma=0.99$ is used for evaluation. A score of 40 or greater will receive full credit. Your submission should be a function that takes in a state and returns an action.
    \end{enumerate}
\end{question}
\end{document}
