\documentclass{article}
\usepackage{fullpage,amsmath,amsthm,graphicx,enumitem,amsfonts}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{sgame}
\usepackage{subfig}

\usepackage{tikz}
\usetikzlibrary{positioning, shapes, arrows, fit}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}
\newtheorem{question}[thm]{Question}
\newenvironment{solution}{\noindent\textit{Solution:}}{}

\title{ASEN 5264 Decision Making under Uncertainty\\
       Exam 3: POMDPs and Games}

\begin{document}
\maketitle


\noindent \textbf{Instructions:} Clearly indicate your final answers and \textbf{briefly justify all answers with text, mathematical expressions, and/or calculations}. If you do not understand how to do a problem, skip it and move on so that you have time to attempt all problems. You may consult any static source, but you may NOT communicate with any person except the instructor or TA, and you may not use LLMs such as ChatGPT.
\\
\\
\noindent\textbf{Important:} Please include the following statement along with your signature (typed or handwritten) on the exam: \textbf{``I affirm that I completed this exam without the use of any artificial intelligence tool such as ChatGPT or Github Copilot.''}

\clearpage

\noindent\textbf{Note:} Question 1 has been removed from this exam because it was added to Homework 5.

\begin{question}(45 points)
    Two countries are deciding whether to pursue protectionist ($P$) or free trade ($F$) policies.
    One model focuses on the need to protect key industries for national security. In this model a country receives a payoff of 1 if they protect these industries and a payoff of -1 if only the other country protects them, resulting in the following payoff matrix:
    \begin{center}
    \begin{game}{2}{2}
        & $P$ & $F$ \\
        $P$ & $1, 1$ & $-1, 1$ \\
        $F$ & $1, -1$ & $0, 0$
    \end{game}
    \end{center}
    \begin{enumerate}[label=\alph*)]
        \item Are there any dominant strategy equilibria in this game? If so, what are they? Briefly justify your answer.
        \\ \\ \noindent \textbf{Solution: }
        This game matrix contained a typo and should have been written

        \begin{game}{2}{2}
            & $P$ & $F$ \\
            $P$ & $1, 1$ & $1, -1$ \\
            $F$ & $-1, 1$ & $0, 0$
        \end{game}

        For this reason we accepted three approaches:

        \textbf{Approach 1}: For the new correctly-posed game, for both players, P is a best response if the other player plays P and if the other player plays F. So \fbox{(P,P) is the only dominant strategy equilibrium.}

        \textbf{Approach 2}: Some students used the given game matrix, in which case for either player, both P and F are best responses to P, and F is a best response to F. Thus, F is a dominant strategy for both players, so \fbox{(F, F) is a dominant strategy equilibrium}.

        \textbf{Approach 3}: Some students reasoned that the typo indicated that the column player is player 1 and row player is player 2.
        Letting the first country correspond to the columns, the P action dominates regardless of the opponent choice for both countries. Thus, the policy pair \fbox{(P,P) is the only dominant strategy equilibrium}. \\
        \item Are there any pure Nash equilibria in this game? If so, what are they? Briefly justify your answer.
        \\ \\ \noindent \textbf{Solution: } A dominant strategy equilibrium is a type of pure Nash equilibrium, so, if Approach 1 or 3 was taken above, \fbox{(P, P)} is the only pure Nash equilibrium. If Approach 2 was taken, \fbox{(P,P) and (F, F)} are both pure Nash equilibria.\\
    \end{enumerate}
    A second model focuses on comparative advantage and the larger effective size of the economy that results from free trade. In this model a country receives a payoff of 1 if they pursue free trade and a payoff of 1 if the other country pursues free trade. These payoffs add together if both countries pursue free trade. There are no other payoffs in this model.
    \begin{enumerate}[label=\alph*), resume]
        \item What is the payoff matrix for this model?
        \\ \\ \noindent \textbf{Solution: }
        \begin{center}
        \begin{game}{2}{2}
        & $P$ & $F$ \\
        $P$ & $0, 0$ & $1, 1$ \\
        $F$ & $1, 1$ & $2, 2$
        \end{game}
        \end{center}
        \item Are there any dominant strategy equilibria in this game? If so, what are they? Briefly justify your answer.
        \\ \\ \noindent \textbf{Solution: } Yes, the F action dominates all others, both countries have a dominant strategy of pursuing free trade. Thus, the policy pair (F,F) is a dominant strategy equilibrium
        \item Are there any pure Nash equilibria in this game? If so, what are they? Briefly justify your answer.
        \\ \\ \noindent \textbf{Solution: }
        A dominant strategy equilibrium is a type of pure Nash equilibrium, so the policy pair (F,F) is the only pure Nash equilibrium.
    \end{enumerate}
    A third model that takes into account a variety of factors is the following:
    \begin{center}
    \begin{game}{2}{2}
        & $P$ & $F$ \\
        $P$ & $8, 8$ & $ 9,  6$ \\
        $F$ & $6, 9$ & $10, 10$
    \end{game}
    \end{center}
    \begin{enumerate}[label=\alph*), resume]
        \item Are there any dominant strategy equilibria in this game? If so, what are they? Briefly justify your answer.
        \\ \\ \noindent \textbf{Solution: } Let the first country correspond to the rows. Each player wants to match the action of the other, so there is no dominant strategy equilibrium. \\
        \item Are there any Nash equilibria in this game? If so, what are they? Make sure to include all Nash equilibria and describe the policies used by both players precisely. Breifly justify your answer.
        \\ \\ \noindent \textbf{Solution: }
        Yes, there are two pure Nash equilibria, at (P,P) and (F,F). Each country would receive a lower payoff by deviating from the other's policy. There is also a mixed-Nash equilibrium where each player chooses F with probability $\frac{2}{3}$, and P with probability $\frac{1}{3}$. The derivation is given below. Setting up the system of equations for the first country's indifference to the second's policy:
        \begin{align*}
            8\pi_2(P) + 9\pi_2(F) &= U\\
            6\pi_2(P) + 10\pi_2(F) &= U\\
            \pi_2(P) + \pi_2(F) &= 1\\
        \end{align*}
        Solving for $\pi_2$,
        \begin{align*}
            8\pi_2(P) + 9(1-\pi_2(P)) &= 6\pi_2(P) + 10(1-\pi_2(P))\\
            -\pi_2(P) + 9 &= 10 - 4\pi_2(P)\\
            \pi_2(P) &= \frac{1}{3}\\
            \pi_2(F) &= \frac{2}{3}
        \end{align*}
        The second country's indifference to the first yeilds the equations
        \begin{align*}
            8\pi_1(P) + 9\pi_1(F) &= U\\
            6\pi_1(P) + 10\pi_1(F) &= U\\
            \pi_1(P) + \pi_1(F) &= 1\\
        \end{align*}
        Which in turn yield $\pi_1(P)= 1/3$ and $\pi_1(F) = 2/3$.
    \end{enumerate}
\end{question}
\begin{question} (10 points)
    Suppose that Alice and Bob are playing the 5-card version of ``Goofspiel'' or ``Game of Pure Strategy'' discrete Markov game played in class. Alice has computed a Nash equilibrium for the game and she shares her Nash equilibrium policy, $\pi^1_A$, with Bob.
    \begin{enumerate}[label=\alph*)]
        \item If Bob knows the $(I, S, A, T, R, \gamma)$ model of the game and Alice's policy $\pi^1_A$, describe in two or three sentences and equations how Bob can compute a best response policy with a computer.
        \\ \\ \noindent \textbf{Solution: } Bob can form an MDP using the given model parameters M' = $(S,A^{Bob},T',R',\gamma)$ with \begin{equation*}
            T'(s'|s,a^{Bob}) = \sum_{a^{Alice}}T(s'|s,a^{Bob},a^{Alice})\pi^1_A(a^{Alice}|s)
        \end{equation*}
        and
        \begin{equation*}
            R'(s, a^{Bob}) = \sum_{a^{Alice}} R^{Bob}(s, a^{Bob}, a^{Alice}) \pi^1_A(a^{Alice} | s)
        \end{equation*}
        and solve the MDP for the best response policy using any of the MDP solvers we have covered in this course.
        \item If Bob then plays the best response policy computed in the manner described above against $\pi^1_A$, is the resulting joint policy guaranteed to be a Nash equilibrium? Briefly justify your answer.
        \\ \\ \noindent \textbf{Solution: } \fbox{No}. Though Bob's policy is a best response to Alice's, Alice's policy may not be a best response to Bob's. For example, even though the Nash equilibrium (shown in class) consists of mixed policies, Bob may calculate a deterministic best response. Then Alice may have a best response to that policy that is not a Nash equilibrium policy.\\
    \end{enumerate}
\end{question}

\end{document}
